Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R

### 2023-11-15 draft_paper.qmd
Paper draft is now with an outline

>>>>

Measurement lays an important foundation of psychological science.

# A Brief Overview of Item Response Theory

# Graded Response Model

# Assumptions and Key Concepts

# An Illustrative Example of Graded Response Model: The Right Wing Authoritarianism (RWA) Scale
## A Brief Overview of the Altemeyer's RWA Scale
## Step 1: Preparation
## Step 2: Inspecting Key Descriptive Statistics
## Step 3: Examining Dimensionality
## Step 4: Model Estimation, Parameters, and Fit Statistics
## Step 5: Model Residuals
## Step 6: IRT Plots
## Step 7: Computing Reliability

# Conclusions
